---
title: "600_4_Quarto"
author: "Tomaz Kastrun"
date: 2025-03-26
description: "Sample pptx made from Quarto R"
format:
  pptx:
    reference-doc: template_pptx.pptx
    slide-number: true
    transition: slide
editor: visual
params:
  cyl: 4
---

# Analysis of mtcars

## General data view

Analysis of the mtcars dataset:

```{r}
#| label: fig-1_drat_wt_cyl_4
#| warning: false
#| echo: false
#| eval: true


library(ggplot2)
library(tidyverse)

mtcars %>%
  filter(cyl == params$cyl) %>%
ggplot(aes(drat, wt)) + 
  geom_point() + 
  geom_smooth(method = "loess")
```

## Data understanding

You need to include

-   **understanding** of markdown
-   general approach for **analysis**

## Code {background-image="background.png"}

Check the first three lines of cross-tabulation of **mpg** and **cyl**.

```{r}
#| warning: false
#| echo: false
#| eval: true

head(table(mtcars$mpg, mtcars$cyl),3)
```

## Checking data 

We can check first 6 rows and first 6 columns.

```{r}
#| warning: false
#| echo: false
knitr::kable(
  mtcars[1:6, 1:6], caption = 'A subset of mtcars.'
)
```

## Comparing cyl

<div class="centered">
Comparing 8 and 6 *cyl* on *drat* and wt scatterplot.
</div>

::::: columns
::: {.column width="40%"}
```{r}
mtcars %>%
  filter(cyl == 8) %>%
ggplot(aes(drat, wt)) + 
  geom_point() + 
  geom_smooth(method = "loess")
```
:::

::: {.column width="60%"}
```{r}
mtcars %>%
  filter(cyl == 6) %>%
ggplot(aes(drat, wt)) + 
  geom_point() + 
  geom_smooth(method = "loess")
```
:::
:::::


## Conclusion


::::: columns

::: {.column width="33%"}
```{r}

library(ggforce)
percentage_done <- 0.95
fake_dat <- tibble(
  part = c("Complete", "Incomplete"),
  percentage = c(percentage_done, 1 - percentage_done),
  start = lag(percentage, default = 0) * pi,
  end = start + percentage * pi
)

gauge_plot <- fake_dat |>
  ggplot() +
  geom_arc_bar(
    aes(
      x0 = 1,
      y0 = 1,
      fill = part,
      start = start - pi / 2,
      end = end - pi / 2,
      r0 = 0.75,
      r = 1
    )
  ) +
  coord_fixed()

labeled_gauge_plot <- gauge_plot +
  annotate(
    "text",
    x = 1,
    y = 1,
    label = glue::glue("{percentage_done * 100}% complete"),
    size = 16,
    family = "Source Sans Pro",
    fontface = "bold",
    color = "#009E73",
    vjust = 0
  ) +
  labs(
    title = "This is a gauge plot",
    subtitle = "It was created in ggplot and shows you how much of your goal\nyou have already achieved."
  )
themed_gauge_plot <- labeled_gauge_plot +
  theme_void() +
  theme(
    legend.position = "none",
    plot.title = element_text(
      family = "Source Sans Pro", size = 28, face = "bold"
    ),
    plot.subtitle = element_text(family = "Source Sans Pro", size = 18)
  )

themed_gauge_plot +
  scale_fill_manual(
    values = c("Complete" = "#009E73", "Incomplete" = "grey80")
  )
```
:::


::: {.column width="33%"}
```{r}

library(ggforce)
percentage_done <- 0.65
fake_dat <- tibble(
  part = c("Complete", "Incomplete"),
  percentage = c(percentage_done, 1 - percentage_done),
  start = lag(percentage, default = 0) * pi,
  end = start + percentage * pi
)

gauge_plot <- fake_dat |>
  ggplot() +
  geom_arc_bar(
    aes(
      x0 = 1,
      y0 = 1,
      fill = part,
      start = start - pi / 2,
      end = end - pi / 2,
      r0 = 0.75,
      r = 1
    )
  ) +
  coord_fixed()

labeled_gauge_plot <- gauge_plot +
  annotate(
    "text",
    x = 1,
    y = 1,
    label = glue::glue("{percentage_done * 100}% complete"),
    size = 16,
    family = "Source Sans Pro",
    fontface = "bold",
    color = "#009E73",
    vjust = 0
  ) +
  labs(
    title = "This is a gauge plot",
    subtitle = "It was created in ggplot and shows you how much of your goal\nyou have already achieved."
  )
themed_gauge_plot <- labeled_gauge_plot +
  theme_void() +
  theme(
    legend.position = "none",
    plot.title = element_text(
      family = "Source Sans Pro", size = 28, face = "bold"
    ),
    plot.subtitle = element_text(family = "Source Sans Pro", size = 18)
  )

themed_gauge_plot +
  scale_fill_manual(
    values = c("Complete" = "#009E73", "Incomplete" = "grey80")
  )
```
:::

:::::
