---
title: example with cell blocks
format: 
  html:
    fig-align: center
    fig-width: 4
    fig-height: 4
    fig-format: png
execute:
  echo: false
  cache: true
---

```{r}
#| label: library
library(tidyverse)
library(gapminder)
```

```{r}
#| label: functions
# A function to scale input to 0-1
scale_01 <- function(x){
  (x - min(x, na.rm = TRUE)) / diff(range(x, na.rm = TRUE))
}
```

```{r}
#| label: read-data
gapminder <- gapminder::gapminder
```

```{r}
r_heights <- c(153, 151, 156, 160, 171)
r_mean <- mean(r_heights)
```

The mean of these heights is `{r} r_mean`

```{r}
#| label: gg-oz-gapminder
#| fig-cap: "Life expectancy from 1952 - 2007 for Australia. Life expentancy increases steadily except from 1962 to 1969. We can safely say that our life expectancy is higher than it has ever been!"
library(ggplot2)
library(dplyr)

gapminder |>
  filter(country == "Australia") |>
  ggplot(aes(x = lifeExp,
             y = year)) + 
  geom_point()
```

And some additional data:

```{r}
top_gap <- head(gapminder)

knitr::kable(top_gap)
```

adding table:

```{r}
knitr::kable(top_gap,
             caption = "The first 6 rows of the dataset, gapminder")
```

```{r}
knitr::kable(top_gap,
             caption = "The first 6 rows of the dataset, gapminder",
             digits = 2)
```

Adding logo:

```{r}
#| label: SID-logo
#| fig-align: center
#| fig-cap: "The R logo which is super neat!"
knitr::include_graphics(here::here( "~/Documents/tomaztk_github/R_Data_manipulation/Session05/R_logo.svg"))

```

Or like this: ![The R Logo](https://upload.wikimedia.org/wikipedia/commons/1/1b/R_logo.svg){fig-alt="A R logo." fig-align="left" width="20%"}

::: {#fig-logos layout-ncol="2"}
![R_left](R_logo.svg){#fig-logo_left}

![R_right](R_logo.svg){#fig-logo_right}

Two logos
:::

And now four logos:

::: {layout-nrow="2"}
![R_left](R_logo.svg){width="50%"}

![R_right](R_logo.svg){width="50%"}

![Another R](R_logo.svg){width="50%"}

![Yet Another](R_logo.svg){width="50%"}
:::

# Callout Blocks

::: callout-note
Note that there are five types of callouts, including: `note`, `warning`, `important`, `tip`, and `caution`.
:::

::: callout-tip
## Tip with Title

This is an example of a callout with a title and the type Tip!
:::

::: {.callout-caution collapse="true"}
## Expand To Learn About Collapse

This is an example of a 'folded' caution callout that can be expanded by the user. You can use `collapse="true"` to collapse it by default or `collapse="false"` to make a collapsible callout that is expanded by default.
:::

::: {.callout-note appearance="simple"}
## Pay Attention

Using callouts is an effective way to highlight content that your reader give special consideration or attention.
:::

::: {#tip-example .callout-tip}
## Cross-Referencing a Tip

Add an ID starting with `#tip-` to reference a tip.
:::

See @tip-example...
