---
title: "500_1_Quarto"
format: html
editor: visual
---

# Head Title

## 1. Title

### 1.1. Subtitle

*italic* and **bold**

## 2. Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

## 3. Creating graphs

```{r}
# graphs
library(ggplot2)
library(tidyverse)

# I have when percentages in pie do not sum to 100%
data.frame(work = c(rep("Being Productive", 1), 
                    rep("Being Frustrated", 1), 
                    rep("Waiting",1)),   #and being Flustered", 1)),
                   amnt = c(0.03, 0.17, 0.81)) %>%
ggplot( aes(x="", y=amnt, group=work, color=work, fill=work)) +
  geom_bar(stat = "identity") +
  coord_polar("y", start=9.9)  +
  ggtitle("Working") + 
  xlab("") + ylab("") +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid  = element_blank(),
        legend.title=element_blank(),
        panel.background = element_rect(fill = "white",
                                        colour = "white",
                                        linetype = "solid")
        #,legend.position="bottom"
        )

```

## Loading packages

In Packages...

```{r}
library(tidyverse)
library(nycflights13)
```

and persisting data

```{r}
tt<-nycflights13::flights
?flights
View(flights)
View(tt)
```

## Example Table

```{r}
# Create a data frame
data <- data.frame(
  Name = c("Alice", "Bob", "Charlie", "David"),
  Age = c(25, 30, 35, 40),
  City = c("New York", "Los Angeles", "Chicago", "Houston")
)
```

### Viewing data

```{r}
View(data)
```
