---
title: "Poročilo o mtcars"
author: "Tomaž Kaštrun"
date: 2025-03-26
editor: visual
description: "Podrobno poročilo med city in cyl variablami"
format:
  html:
    toc: true        # Table of contents
    toc-depth: 2     # Number of TOC levels
    number-sections: true
    theme: cosmo     # Themes: cosmo, flatly, darkly, etc.
    highlight-style: github
---

# Primerajava distribicj z dvema različnima perspektivama

## Podatki

Podatki so zajeti za leto 2023.

```{r}
#| echo: false
#| warning: false
library(tidyverse)
library(gt)

mtcars <- mtcars
mpg2 <- ggplot2::mpg

```

## Perspektiova 1

@fig-cyl-city shows the impact of driving in the city (distance) based on the number of cylders.

```{r}
#| echo: false
#| label: fig-cyl-city
#| fig-cap: "City drive with type of Cylinders"
#| warning: false
mpg2 %>%
  ggplot(aes(as.factor(cyl), cty)) + 
  geom_boxplot()  
```

## Perspektiva 2

@fig-cyl-city_2 shows the impact of driving in the city (distance) based on the number of cylders with all values without missings.

```{r}
#| echo: false
#| label: fig-cyl-city_2
#| fig-cap: "corrected graph: City drive with type of Cylinders"
mpg2 %>%
  ggplot(aes(cyl, cty)) + 
  geom_boxplot(aes(group = cut_width(cyl, 1)))  
```

Zaključek: Grafa se razlikujeta na x-osi z vrednostmi.

## Facets

```{r}
#| echo: false
#| warning: false
mpg3 <- subset(mpg, cyl != 5 & drv %in% c("4", "f") & class != "2seater")

ggplot(mpg3, aes(displ, hwy)) +
  geom_point() + 
  facet_wrap(~class, ncol = 3)
```

## Avg City usage per gallon

```{r}
#| echo: false
#| warning: false
avg_cty <- mean(mpg2$cty)
```

With the average of city distance per gallon is `{r} avg_cty`.

and the formula for calculation is $$
\sum_{i = 1}^{n}{\frac{x_i}{n}}
$$

## Prikaz tabelaričnih podatkov

Pregled podatkov

```{r results='asis'}
#| echo: false
library(gt)
library(tidyverse)
table_3 <- mtcars %>% 
  mutate(
    datetime = seq(
      from = as.POSIXct("2025-01-01 00:00:00"),
      by = "1 hour",
      length.out = n()
    )
    ,timedate = seq(
      from = as.POSIXct("2025-01-01 00:00:00"),
      by = "1 hour",
      length.out = n()
    )
  ) %>%
  head(5) %>% 
  gt() %>% 
  fmt_number(
    columns = c(mpg, wt),
    decimals = 2
  ) %>% 
  fmt_currency(
    columns = c(disp),
    currency = "EUR"
  ) %>%
  fmt_percent(
    columns = drat, 
    decimals = 0
  ) %>%
  fmt_date (
    columns = datetime,
    date_style = "day_m"
  )  %>%
  fmt_time (
    columns = timedate,
    time_style = "h_m_p" #"hm"
    #locale = "sl"
  )
print(table_3)
```

## Končne zaključke

errtwe werwerw
